DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-06-06 manuscript/manuscript.tex
formatting legends and adding png figure for fringillidae example

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4844}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and congruified and mapped age data to nodes in this chosen topology (Table \ref{tbl:table1}).
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated (Table \ref{tbl:table2}) and used as calibrations to date the tree topology using the BLADJ algorithm.
As expected, more inclusive nodes (e.g., node ``n1'') have more variance in age data than less inclusive nodes (e.g., node ``n5'').
Age data for node ``n2'' was excluded as final calibration because it is older than age data of the more inclusive node ``n1'' (Fig. \ref{fig:figure2}C4).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    FIGURE 4    %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\includegraphics{../figures/figure-fringillidae/median_and_calibration_ages_simple.png}
\caption{Fringillidae median summary chronogram generated with DateLife. It has 256 tips and 233 nodes.}
\label{fig:fringillidages}
\end{figure}

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Tree; Phylogeny; Scaling; Dating; Ages; Divergence times; Open Science; Congruification; Supertree; Calibrations; Secondary calibrations\newline\indent Word count: 4845}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\emph{\textbf{Summarizing search results.-}}
DateLife obtained OpenTree's synthetic tree topology for these taxa (Fig. \ref{fig:figure2}C), and congruified and mapped age data to nodes in this chosen topology (Table \ref{tbl:table1}).
The name processing step allowed including five data points for node ``n4'' (parent of \emph{Schoeniclus elegans}; Fig. \ref{fig:figure2}A) that would not have had any data otherwise due to name mismatch.
Age summary statistics per node were calculated (Table \ref{tbl:table2}) and used as calibrations to date the tree topology using the BLADJ algorithm.
As expected, more inclusive nodes (e.g., node ``n1'') have more variance in age data than less inclusive nodes (e.g., node ``n5'').
Summary age data for node ``n2'' were excluded as final calibration because they are older than age data of the more inclusive node, ``n1'' (Fig. \ref{fig:figure2}C4).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%    FIGURE 4    %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!h]
\includegraphics{../figures/figure-fringillidae/median_and_calibration_ages-congruified.png}
\caption{Fringillidae median summary chronogram generated with DateLife. It has 256 tips and 233 nodes.}
\label{fig:fringillidages}
\end{figure}
